Concurrent Programming with CXL

### 2020-06-20 book/paper.tex
Latest version

\section*{Exercises}
\begin{enumerate}
\item Write a synchronization module using your own implementation of \texttt{Lock}
(for example, using Peterson's algorithm or using \texttt{swap}) and run the code in
Figure~\ref{fig:incfixed} using your own module.
\end{enumerate}

>>>>

\section*{Exercises}
\begin{enumerate}
\item Write a synchronization module using your own implementation of \texttt{Lock}
(for example, using Peterson's algorithm or using \texttt{swap}).
\item
Run Figure~\ref{fig:incfixed} using (1) \texttt{synch}, (2), \texttt{synchS},
and (3) your own module.  Report how many states were explored for each
version of the module.
\end{enumerate}
